Downward shortwave solar irradiance enhancement by clouds.

### 2024-05-21 article/article.Rmd
Commit 2024-05-21 19:13

The use of the actual modeled values of clear sky GHI, described above , can not provide us with
a robust method to distinguish the CE cases, due to the limited accuracy of the input
data. Our main focus was to positively identify over irradiance events from CEs, 
so we created an upper envelope of the clear sky irradiance,

.............................

above which, any GHI value can safely attributed to CE.  We evaluated the performance
of the modeled clear radiation for each of atmospheric level of clearness, as
reference, in order to conclude which is the most appropriate.

To select the exact values of these thresholds factors (Equation \ref{eq:CE4}), we
implemented an empirical method, by manual inspection of the CE identification, on
specially selected days from the whole dataset.  We used seven sets of selected days,
with characteristics relevant to the efficiency of the identification threshold.
These sets were random groups of about 20 to 30 days with the following
characteristics:
(a) the largest over irradiance CE events,
(b) the largest daily total over irradiance,
(c) without clouds (by implementing a clear sky identification algorithm as discussed in @Natsis2023),
(d) without clouds and without EC events,
(e) with at least $60\,\%$ of the day length without clouds and some EC events,
(h) random days and
(i) some manual selected days that were included during the manual inspection.
Where it was needed, for some of the edge cases, we also used images from a sky-cam,
to further aid the decisions of the manual inspection.

After evaluating the modeled clear radiation for the different atmospheric
conditions, in relation to the measured GHI data, we choose as a representative of
the clear sky radiation, the case where
$\tau_{\text{cs}} = \tau_{500\text{nm}} - 1\sigma$ and $w_{h\text{cs}} = w_h - 1\sigma$
($\text{GHI}_\text{CSm}$).
These values represent a typical atmosphere in Thessaloniki with low load of aerosols
and humidity, which are the main factor that attenuate the GHI, excluding clouds.  To
create the limit of CE identification, we created a two branched threshold, as a
function of SZA. A constant factor for low SZAs, and a higher ramped factor for
higher SZAs (Equation\nobreakspace\ref{eq:CE4}).
This is the criterion of our CE identification.
<!--
\begin{equation}
\text{CE}_\text{Threshold} = \begin{cases}
`r C4_cs_ref_ratio`, & \text{$\theta \leq `r C4_lowcut_sza`^\circ$}\\
\frac{`r C4_cs_ref_ratio` - `r C4_lowcut_ratio`}{`r C4_lowcut_sza` - `r 90 - BIO_ELEVA`} \cdot (\theta- `r 90 - BIO_ELEVA`) + `r C4_lowcut_ratio` , & \text{$ `r 90 - BIO_ELEVA`^\circ > \theta > `r C4_lowcut_sza`^\circ$}\\
\text{Excluded measurements}, & \theta > `r 90 - BIO_ELEVA`^\circ
\end{cases}\label{eq:CE4a}
\end{equation}
where: $\theta$ solar zenith angle.
-->
<!--
\begin{equation}
\text{CE} : \begin{cases}
 \text{GHI}_\text{i} > `r C4_cs_ref_ratio` \cdot \text{GHI}_\text{mCSi}, & \text{$\theta \leq `r C4_lowcut_sza`^\circ$}\\
\text{GHI}_\text{i} > \left ({ `r C4_lowcut_ratio` + \frac{`r C4_cs_ref_ratio` - `r C4_lowcut_ratio`}{`r C4_lowcut_sza` - `r 90 - BIO_ELEVA`} \cdot (\theta- `r 90 - BIO_ELEVA`) } \right ) \cdot \text{GHI}_\text{mCSi}, & \text{$ `r 90 - BIO_ELEVA`^\circ > \theta > `r C4_lowcut_sza`^\circ$}\\
\text{Excluded measurements}, & \theta > `r 90 - BIO_ELEVA`^\circ
\end{cases}\label{eq:CE4b}
\end{equation}
where: $\theta$ is the solar zenith angle, $\text{GHI}_\text{i}$ the measured
irradiance, and $\text{GHI}_\text{mCSi}$ the selected modelled clear sky irradiance.
-->
<!-- \begin{equation} -->
<!-- \text{CE} : \text{E}_\text{i} > \text{E}_\text{CSlim,i}, \text{where} \begin{cases} -->
<!--  \text{E}_\text{CSlim,i} = `r C4_cs_ref_ratio` \cdot \text{E}_\text{CSm,i}, & \text{$\theta \leq `r C4_lowcut_sza`^\circ$}\\ -->
<!-- \text{E}_\text{CSlim,i} = \left ({ `r C4_lowcut_ratio` + \frac{`r C4_cs_ref_ratio` - `r C4_lowcut_ratio`}{`r C4_lowcut_sza` - `r 90 - BIO_ELEVA`} \cdot (\theta- `r 90 - BIO_ELEVA`) } \right ) \cdot \text{E}_\text{CSm,i}, & \text{$ `r 90 - BIO_ELEVA`^\circ > \theta > `r C4_lowcut_sza`^\circ$}\\ -->
<!-- \text{Excluded measurements}, & \theta > `r 90 - BIO_ELEVA`^\circ -->
<!-- \end{cases}\label{eq:CE4} -->
<!-- \end{equation} -->
<!-- where: $\theta$ is the solar zenith angle, $\text{E}$ the measured -->
<!-- irradiance, $\text{E}_\text{CSm}$ the selected modelled clear sky irradiance, and $i$ each of the one-minute observation. -->

\begin{equation}
\text{CE} : \text{E}_\text{i} > `r C4_GLB_diff_THRES` + `r C4_cs_ref_ratio` \cdot \text{E}_\text{CSm,i} \,\,[W/m^2] \label{eq:CE4}
\end{equation}
where: $\theta$ is the solar zenith angle, $\text{E}$ the measured
irradiance, $\text{E}_\text{CSm}$ the selected modelled clear sky irradiance, and $i$ each of the one-minute observation.

<!-- reasoning for cretria -->
We have to note, that the differentiation of the threshold factor was needed, because
of the high irradiance values we observed, early in the morning and late in the
afternoon. We have confirmed, by inspecting images from the sky cam, that we have
duration of elevated irradiance, either due to the clearness of the atmosphere, or some
interferences by reflections on nearby bright surfaces. Although, these cases may
mask some of the CE events. The actual CE events, produce higher irradiance and thus
are identified as such. As a side effect, the reported OIR will be slight
underestimated for those SZAs, but the overall contribution of those cases to the
total daily energy, is minimal due the low occurrences and the lower irradiances.

>>>>

Our main focus was to positively identify over irradiance events related to CEs.  For
this reason we had to select an appropriate set of atmospheric parameterization, in
Libradtran, and define an relevant threshold for the CE identification.  The
selection of the atmospheric parameterization will provide us with a reference, that
has a good agreement with the clear sky conditions. Additional, with the
implementation of the long term change, as described above, it will be able to align
well with most of the natural variation of the physical quantity.  The selection of
adequate threshold, will also allow us to have a robust method to distinguish the CE
cases, which will compensate for the limited accuracy of the input data, and the
natural variability of the atmosphere.

First, we evaluated the performance of the modelled clear radiation, for each of
the atmospheric level of clearness we have created as reference, in relation to the
measured GHI data, and choose as a representative of the clear sky radiation, the
case where
$\tau_{\text{cs}} = \tau_{500\text{nm}} - 1\sigma$ and $w_{h\text{cs}} = w_h - 1\sigma$
($\text{GHI}_\text{CSm}$).
These values represent a typical atmosphere in Thessaloniki, with low load of
aerosols and humidity, which are the main factor that attenuate the GHI, excluding
clouds.  To create the upper limit of CE identification, we used a value relative to
clear sky irradiance
($`r 100*(C4_cs_ref_ratio-1)`\,\%$)
with an additional constant offset of
$`r C4_GLB_diff_THRES`\,\text{W}/\text{m}^2$,
as described in Equation\nobreakspace\ref{eq:CE4}).
\begin{equation}
\text{CE} : \text{E}_\text{i} > `r C4_GLB_diff_THRES` + `r C4_cs_ref_ratio` \cdot \text{E}_\text{CSm,i} \,\,[\text{W}/\text{m}^2] \label{eq:CE4}
\end{equation}
where: $\text{E}$ the measured irradiance, $\text{E}_\text{CSm}$ the selected
modelled clear sky irradiance, and $i$ each of the one-minute observation.  This is
the criterion of our CE identification.

In the process of defining the above details, we implemented an empirical method, by
manual inspection of the CE identification, on specially selected days from the whole
dataset.  We used seven sets of selected days, with characteristics relevant to the
efficiency of the identification threshold.  These sets were random groups of about
20 to 30 days with the following
characteristics:
(a) the largest over irradiance CE events,
(b) the largest daily total over irradiance,
(c) without clouds (by implementing a clear sky identification algorithm as discussed in @Natsis2023),
(d) without clouds and without EC events,
(e) with at least $60\,\%$ of the day length without clouds and some EC events,
(h) random days and
(i) some manual selected days that were included during the manual inspection.
Where it was needed, for some of the edge cases, we also used images from a sky-cam,
to further aid the decisions of the manual inspection.

<!--
\begin{equation}
\text{CE}_\text{Threshold} = \begin{cases}
`r C4_cs_ref_ratio`, & \text{$\theta \leq `r C4_lowcut_sza`^\circ$}\\
\frac{`r C4_cs_ref_ratio` - `r C4_lowcut_ratio`}{`r C4_lowcut_sza` - `r 90 - BIO_ELEVA`} \cdot (\theta- `r 90 - BIO_ELEVA`) + `r C4_lowcut_ratio` , & \text{$ `r 90 - BIO_ELEVA`^\circ > \theta > `r C4_lowcut_sza`^\circ$}\\
\text{Excluded measurements}, & \theta > `r 90 - BIO_ELEVA`^\circ
\end{cases}\label{eq:CE4a}
\end{equation}
where: $\theta$ solar zenith angle.
-->
<!--
\begin{equation}
\text{CE} : \begin{cases}
 \text{GHI}_\text{i} > `r C4_cs_ref_ratio` \cdot \text{GHI}_\text{mCSi}, & \text{$\theta \leq `r C4_lowcut_sza`^\circ$}\\
\text{GHI}_\text{i} > \left ({ `r C4_lowcut_ratio` + \frac{`r C4_cs_ref_ratio` - `r C4_lowcut_ratio`}{`r C4_lowcut_sza` - `r 90 - BIO_ELEVA`} \cdot (\theta- `r 90 - BIO_ELEVA`) } \right ) \cdot \text{GHI}_\text{mCSi}, & \text{$ `r 90 - BIO_ELEVA`^\circ > \theta > `r C4_lowcut_sza`^\circ$}\\
\text{Excluded measurements}, & \theta > `r 90 - BIO_ELEVA`^\circ
\end{cases}\label{eq:CE4b}
\end{equation}
where: $\theta$ is the solar zenith angle, $\text{GHI}_\text{i}$ the measured
irradiance, and $\text{GHI}_\text{mCSi}$ the selected modelled clear sky irradiance.
-->
<!-- \begin{equation} -->
<!-- \text{CE} : \text{E}_\text{i} > \text{E}_\text{CSlim,i}, \text{where} \begin{cases} -->
<!--  \text{E}_\text{CSlim,i} = `r C4_cs_ref_ratio` \cdot \text{E}_\text{CSm,i}, & \text{$\theta \leq `r C4_lowcut_sza`^\circ$}\\ -->
<!-- \text{E}_\text{CSlim,i} = \left ({ `r C4_lowcut_ratio` + \frac{`r C4_cs_ref_ratio` - `r C4_lowcut_ratio`}{`r C4_lowcut_sza` - `r 90 - BIO_ELEVA`} \cdot (\theta- `r 90 - BIO_ELEVA`) } \right ) \cdot \text{E}_\text{CSm,i}, & \text{$ `r 90 - BIO_ELEVA`^\circ > \theta > `r C4_lowcut_sza`^\circ$}\\ -->
<!-- \text{Excluded measurements}, & \theta > `r 90 - BIO_ELEVA`^\circ -->
<!-- \end{cases}\label{eq:CE4} -->
<!-- \end{equation} -->
<!-- where: $\theta$ is the solar zenith angle, $\text{E}$ the measured -->
<!-- irradiance, $\text{E}_\text{CSm}$ the selected modelled clear sky irradiance, and $i$ each of the one-minute observation. -->

<!-- reasoning for cretria -->
<!-- We have to note, that the differentiation of the threshold factor was needed, because
<!-- of the high irradiance values we observed, early in the morning and late in the
<!-- afternoon. 
<!-- We have confirmed, by inspecting images from the sky cam, that we have
<!-- duration of elevated irradiance, either due to the clearness of the atmosphere, or some
<!-- interferences by reflections on nearby bright surfaces. Although, these cases may
<!-- mask some of the CE events. The actual CE events, produce higher irradiance and thus
<!-- are identified as such. As a side effect, the reported OIR will be slight
<!-- underestimated for those SZAs, but the overall contribution of those cases to the
<!-- total daily energy, is minimal due the low occurrences and the lower irradiances.
-->
